Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing

### 2020-02-06 Dissonance_Santiago_v2/Dissonance_Santiago_v2.Rmd
Reorganized folder structure and created a new version to revise the paper after receiving reviewer comments from Journal of Transportation and Health.

journal: "Journal of Transportation & Health"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

@@

# Load packages used in this document

library(rticles)
library(readxl)
library(tidyverse)
library(rgdal)
library(sf)
library(ggmosaic)
library(ggthemes)
library(kableExtra)
library(gridExtra)
```

@@

age_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = AGE)) +
  geom_bar() +
  theme_tufte() +
  xlab("Age of respondents") +
  theme(axis.text.x = element_text(angle = 90))

education_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = EDUCATION)) +
  geom_bar() +
  theme_tufte() +
  xlab("Education level of respondents") +
  theme(axis.text.x = element_text(angle = 90))

income_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = INCOME)) +
  geom_bar() +
  theme_tufte() +
  xlab("Income level of respondents") +
  theme(axis.text.x = element_text(angle = 90))

time_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = TRAVEL_TIME)) +
  geom_bar() +
  theme_tufte() +
  xlab("Duration of regular commute") +
  theme(axis.text.x = element_text(angle = 90))

@@

```{r figure-primary-mode-travel, fig.width= 4, fig.height=6, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:primary-mode-travel}Frequency of primary mode used for regular commute; top panel: all modes, bottom panel: aggregated modes"}
mode_plot1 <- ggplot(data = master, aes(x = factor(USED, levels = c("A", "B", "C", "D", "E", "F", "G", "H"),
                                     labels = c("Car", "Taxi", "Colectivo", "Motorcycle", "Metro", "Bus", "Bicycle", "Walk")))) +
  geom_bar() +
  xlab("Primary Mode of Travel") +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90))

mode_plot2 <- ggplot(data = Overall_dissonance, aes(x = USED)) +
  geom_bar() +
  xlab("Primary Mode of Travel") +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90))

@@

The preceding analysis suggests that there is significant mode dissonance along various dimensions and for various affective values. This is for the most part in line with previous research, although by examining different affective values individually instead of a summary measure of wellbeing, we are able to differentiate better in terms of how travellers respond to different affects. Less is known about the values that travellers associate with modes _other_ than the one they use. For this reason, after developing a profile of the travelers who experience mode dissonance in the preceding section, we are now interested in the responses of travellers with respect to the modes they tend to associate with various affective values. For this analysis we employ a visualization technique known as a mosaic plot. Mosaic plots are used in the exploration of multivariate categorical data [@Friendly1994mosaic; @Hofmann2000exploring], and they provide visual representations of multi-way contingency tables. The elements of the mosaic plot are called _tiles_, and the dimensions of each tile are proportional to values of variables in the underlying table.

We begin our analysis by plotting primary mode of travel and the modes associated with each affective value (see Figure \ref{fig:mosaic-plots-by-attribute}). The height of tile $j$ in these mosaics corresponds to the proportion of travellers who primarily travel by mode $j$, hence we can see that the most common primary mode of travel in this sample is by public transportation, followed by car, active travel, and other (also see Figure \ref{fig:primary-mode-travel}). Notice that there are some small discrepancies in the heights across affective values: these are caused by a small number of non-responses. Next, the width of the tile $k$ in the mosaics is proportional to the frequency with which a mode was named in relation to affective value $i$. Recall that respondents could nominate more than one mode in response to each affective value, and some did. For this reason, we used sampling weights, so that the total number of responses corresponds to the size of the sample.

@@

```{r figure-mosaic-plots-by-attribute, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}

@@

@@

There are some interesting differences when viewed from the perspective of travellers of different ages (see Figure \ref{fig:mosaic-plots-by-age}). For example, as seen above, active travel is commonly associated with freedom, happiness, and enjoyment, even by car users, but especially by users of public transportation and other modes. However, when we break this down by age, we notice that this tendency weakens as people age, and older travellers increasingly associate these affective values to the car. Furthermore, the tendency to associate status with the car tends to increase with age, with the possible exception of public transport users, for whom other options (possibly taxi), gain status for older travellers (> 54) at the expense of other modes, including the car. In contrast, the car loses in the value of luxury with age, while other options become more commonly associated with feelings of luxury for older respondents, even for car users (Figure 2). Older car users (> 54) show less dissonance in status than in luxury, while active travellers present more dissonance in status than in luxury - and in fact, they more commonly project status in the car.

```{r figure-mosaic-plots-by-attribute-and-age, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}

@@

# Also, use Cochran-Mantel-Haenzel tests
# Freedom
Modes_by_Freedom_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM")))

# Enjoyment
Modes_by_Enjoyment_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT")))

# Happiness
Modes_by_Happiness_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS")))

# Luxury
Modes_by_Luxury_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))

# Status
Modes_by_Status_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))

labels <- c(paste('FREEDOM\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 2) >= 0.001,
                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
                                             " < 0.001")),
            paste('ENJOYMENT\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
                                             " < 0.001")),
            paste('HAPPINESS\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
                                             " < 0.001")),
            paste('LUXURY\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
                                             " < 0.001")),
            paste('STATUS\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
                                             " < 0.001")))

@@

@@

Only two affective values were significant in the preceding analysis when seen from the perspective of education, namely luxury and status. As seen in Figure \ref{fig:mosaic-plots-by-education}, the perceptions of luxury and status are fairly consistent when differentiated by education. Most respondents tend to associate luxury and status to the use of car, albeit this association is stronger for status than for luxury. The second mode most often mentioned in relation to luxury is "other" likely due to the flexibility and convenience (but cost) of using taxis. The exception in this case is the traveller with graduate education who uses active modes. This type of respondent, while still more likely to associate luxury and status with the car, more commonly links active travel to these affects than travellers with lower levels of education. Most public transport users tend to associate luxury and status to the car, however, they associate active modes with status more than the same group with respect to luxury.

```{r figure-mosaic-plots-by-attribute-and-education, echo=FALSE, cache = TRUE, fig.width= 6, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}

@@

>>>>

   journal: "Journal of Transportation & Health"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article

header-includes:
   - \usepackage[margin=1in]{geometry}
   - \usepackage{lineno}
   - \linenumbers
---

@@

# Load packages used in this document
library(ggmosaic)
library(ggthemes)
library(grid)
library(gridExtra)
library(kableExtra)
library(readxl)
library(rgdal)
library(rticles)
library(sf)
library(tidyverse)
```

@@

age_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = AGE, fill = AGE)) +
  geom_bar() +
  theme_tufte() +
  xlab("Age of respondents") +
  scale_fill_viridis_d() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

education_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = EDUCATION, fill = EDUCATION)) +
  geom_bar() +
  theme_tufte() +
  xlab("Education level of respondents") +
  scale_fill_viridis_d() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

income_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = INCOME, fill = INCOME)) +
  geom_bar() +
  theme_tufte() +
  xlab("Income level of respondents") +
  scale_fill_viridis_d() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

time_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = TRAVEL_TIME, fill = TRAVEL_TIME)) +
  geom_bar() +
  theme_tufte() +
  xlab("Duration of regular commute") +
  scale_fill_viridis_d() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

@@

```{r figure-primary-mode-travel, fig.width= 4, fig.height=6, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:primary-mode-travel}Frequency of primary mode used for regular commute; top panel: all modes, bottom panel: aggregated modes"}
mode_plot1 <- ggplot(data = master, aes(x = factor(USED, levels = c("A", "G", "H", "E", "F", "B", "C", "D"),
                                                   labels = c("Car", "Bicycle", "Walk", "Metro", "Bus", "Taxi", "Colectivo", "Motorcycle")),
                                        fill = USED)) +
  geom_bar() +
  xlab("Primary Mode of Travel") +
  scale_fill_manual(values = c("A" = "#F8766D", 
                               "G" = "#00BA38", "H" = "#00BA38", 
                               "E" = "#619CFF", "F" = "#619CFF", 
                               "B" = "#C77CFF", "C" = "#C77CFF", "D" = "#C77CFF")) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

mode_plot2 <- ggplot(data = Overall_dissonance, aes(x = USED, fill = USED)) +
  geom_bar() +
  xlab("Primary Mode of Travel") +
  scale_fill_manual(values = c("Car" = "#F8766D", "Active" = "#00BA38", "Public" = "#619CFF", "Other" = "#C77CFF")) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

@@

The preceding analysis suggests that there is significant mode dissonance along various dimensions and for various affective values. This is for the most part in line with previous research, although by examining different affective values individually instead of a summary measure of wellbeing, we are able to differentiate better in terms of how travellers respond to different affects. Less is known about the values that travellers associate with modes _other_ than the one they use. For this reason, after developing a profile of the travelers who experience mode dissonance in the preceding section, we are now interested in the responses of travellers with respect to the modes they tend to associate with various affective values.

__**For this analysis we employ a visualization technique known as a mosaic plot. Mosaic plots are used in the exploration of multivariate categorical data [@Friendly1994mosaic; @Hofmann2000exploring], and they provide visual representations of multi-way contingency tables. The elements of the mosaic plot are called _tiles_, and the dimensions of each tile are proportional to values of variables in the underlying table.**__

We begin our analysis by plotting primary mode of travel and the modes associated with each affective value (see Figure \ref{fig:bar-plots-by-attribute}). The height of tile $j$ in these mosaics corresponds to the proportion of travellers who primarily travel by mode $j$, hence we can see that the most common primary mode of travel in this sample is by public transportation, followed by car, active travel, and other (also see Figure \ref{fig:primary-mode-travel}). Notice that there are some small discrepancies in the heights across affective values: these are caused by a small number of non-responses. Next, the width of the tile $k$ in the mosaics is proportional to the frequency with which a mode was named in relation to affective value $i$. Recall that respondents could nominate more than one mode in response to each affective value, and some did. For this reason, we used sampling weights, so that the total number of responses corresponds to the size of the sample.

@@

```{r figure-mosaic-plots-by-attribute, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}

@@

```{r figure-bar-plots-by-attribute, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:bar-plots-by-attribute}Plots for affective values; in the y-axis are the number of cases by primary mode of transportation, and in the x-axis are the modes selected for each affective value"}

Attribute_by_ideal <- Modes_by_Attribute %>% 
  drop_na() %>%
  filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"),
         USED != "Other", 
         IDEAL != "Other") %>%
  group_by(IDEAL, ATTRIBUTE, USED) %>%
  summarize(n= sum(WEIGHT)) %>%
  ungroup() %>%
  # rename(MODE = IDEAL) %>%
  mutate(CASE = "IDEAL",
         USED = factor(USED, 
                       levels = c("Car", "Active", "Public"),
                       labels = c("USED: CAR", "USED: ACTIVE", "USED: PUBLIC")))

Attribute_by_used <- Attribute_by_ideal %>%
  group_by(USED, ATTRIBUTE) %>%
  summarize(t = sum(n))

Attribute_by_ideal <- Attribute_by_ideal %>%
  left_join(Attribute_by_used, 
            by = c("USED" = "USED", 
                   "ATTRIBUTE" = "ATTRIBUTE")) %>% 
  mutate(p = n/t)

Attribute_by_ideal_by_mode <- ggplot(data = Attribute_by_ideal,
       aes(x = IDEAL, y = p, fill = IDEAL)) + 
  geom_col() +
  facet_grid(USED ~ ATTRIBUTE) +
  #xlab("Modes associated with affective values") +
  scale_y_continuous(name = "Proportion", 
                     breaks = c(0, 0.5, 1), 
                     limits = c(0, 1)) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom",
        panel.border = element_rect(color = "black", fill = NA),
        axis.title.x = element_blank(),
        legend.title = element_blank())

grid.arrange(Attribute_by_ideal_by_mode, 
             textGrob("Primary Mode of Travel",
                      rot = 270,
                      gp = gpar(fontsize = 11),
                      y = 0.6),
             widths = c(10, 0.5),
             ncol = 2,
             top = "Affective Values",
             bottom = "Modes Associated with Affective Values")
```

@@

There are some interesting differences when viewed from the perspective of travellers of different ages (see Figure \ref{fig:bar-plots-by-age}). For example, as seen above, active travel is commonly associated with freedom, happiness, and enjoyment, even by car users, but especially by users of public transportation and other modes. However, when we break this down by age, we notice that this tendency weakens as people age, and older travellers increasingly associate these affective values to the car. Furthermore, the tendency to associate status with the car tends to increase with age, with the possible exception of public transport users, for whom other options (possibly taxi), gain status for older travellers (> 54) at the expense of other modes, including the car. In contrast, the car loses in the value of luxury with age, while other options become more commonly associated with feelings of luxury for older respondents, even for car users (Figure 2). Older car users (> 54) show less dissonance in status than in luxury, while active travellers present more dissonance in status than in luxury - and in fact, they more commonly project status in the car.

```{r tests-by-attribute-and-age, echo=FALSE, cache = TRUE}

@@

# Also, use Cochran-Mantel-Haenzel tests
# Freedom
Modes_by_Freedom_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM",
                                                               USED != "Other", 
                                                               IDEAL != "Other"), 
                                                 drop.unused.levels = TRUE))

# Enjoyment
Modes_by_Enjoyment_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT",
                                                                 USED != "Other", 
                                                                 IDEAL != "Other"), 
                                                   drop.unused.levels = TRUE))

# Happiness
Modes_by_Happiness_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS",
                                                                 USED != "Other", 
                                                                 IDEAL != "Other"), 
                                                   drop.unused.levels = TRUE))

# Poverty (p = 0.9702)
Modes_by_Poverty_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "POVERTY",
                                                               USED != "Other", 
                                                               IDEAL != "Other"), 
                                                 drop.unused.levels = TRUE))

# Luxury
Modes_by_Luxury_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY",
                                                              USED != "Other", 
                                                              IDEAL != "Other"), 
                                                drop.unused.levels = TRUE))

# Status
Modes_by_Status_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS",
                                                              USED != "Other", 
                                                              IDEAL != "Other"),
                                                drop.unused.levels = TRUE))
```

```{r figure-mosaic-plots-by-attribute-and-age, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}

@@

```{r figure-bar-plots-by-attribute-and-age, echo=FALSE, cache = TRUE, fig.cap="\\label{fig:bar-plots-by-age}Plots for affective values by age; in the y-axis is the proportion in the interval [0, 1], and the x-axis is the mode selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
Attribute_by_ideal_by_age <- Modes_by_Attribute %>% 
  drop_na() %>%
  filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"),
         USED != "Other", 
         IDEAL != "Other") %>%
  group_by(IDEAL, ATTRIBUTE, AGE, USED) %>%
  summarize(n= sum(WEIGHT)) %>%
  ungroup() %>%
  # rename(MODE = IDEAL) %>%
  mutate(CASE = "IDEAL",
         USED = factor(USED, 
                       levels = c("Car", "Active", "Public", "Other"),
                       labels = c("USED: CAR", "USED: ACTIVE", "USED: PUBLIC", "USED: OTHER")))

Attribute_by_ideal <- Attribute_by_ideal_by_age %>%
  group_by(USED, ATTRIBUTE, AGE) %>%
  summarize(t = sum(n))

Attribute_by_ideal_by_age <- Attribute_by_ideal_by_age %>%
  left_join(Attribute_by_ideal, 
            by = c("USED" = "USED", 
                   "ATTRIBUTE" = "ATTRIBUTE", 
                   "AGE" = "AGE")) %>% 
  mutate(p = n/t)

Freedom_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
                           filter(ATTRIBUTE %in% c("FREEDOM"),
                                  USED != "USED: OTHER", 
                                  IDEAL != "Other"),
                         aes(x = IDEAL, y = p, fill = IDEAL)) + 
  geom_col(position = "dodge") +
  facet_grid(USED ~ AGE, shrink = TRUE) +
  xlab("Modes associated with affective values") +
  ylab("Number of cases") +
  theme_tufte() +
  theme(panel.border = element_rect(color = "black", fill = NA)) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        plot.margin = margin(0, 0, 0, 0, "cm"))

Enjoyment_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
                             filter(ATTRIBUTE %in% c("ENJOYMENT"),
                                    USED != "USED: OTHER", 
                                    IDEAL != "Other"),
                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
  geom_col(position = "dodge") +
  facet_grid(USED ~ AGE, shrink = TRUE) +
  xlab("Modes associated with affective values") +
  ylab("Number of cases") +
  theme_tufte() +
  theme(panel.border = element_rect(color = "black", fill = NA)) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom",
        axis.title.x=element_blank(),
        panel.spacing = unit(0.1, "lines"),
        plot.margin = margin(0, 0, 0, 0, "cm"))

Happiness_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
                             filter(ATTRIBUTE %in% c("HAPPINESS"),
                                    USED != "USED: OTHER", 
                                    IDEAL != "Other"),
                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
  geom_col(position = "dodge") +
  facet_grid(USED ~ AGE, shrink = TRUE) +
  xlab("Modes associated with affective values") +
  ylab("Number of cases") +
  theme_tufte() +
  theme(panel.border = element_rect(color = "black", fill = NA)) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom",
        axis.title.x=element_blank(),
        panel.spacing = unit(0.1, "lines"),
        plot.margin = margin(0, 0, 0, 0, "cm"))

Luxury_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
                          filter(ATTRIBUTE %in% c("LUXURY"),
                                 USED != "USED: OTHER", 
                                 IDEAL != "Other"),
                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
  geom_col(position = "dodge") +
  facet_grid(USED ~ AGE, shrink = TRUE) +
  xlab("Modes associated with affective values") +
  ylab("Number of cases") +
  theme_tufte() +
  theme(panel.border = element_rect(color = "black", fill = NA)) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom",
        axis.title.x=element_blank(),
        panel.spacing = unit(0.1, "lines"),
        plot.margin = margin(0, 0, 0, 0, "cm"))

Status_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
                          filter(ATTRIBUTE %in% c("STATUS"),
                                 USED != "USED: OTHER", 
                                 IDEAL != "Other"),
                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
  geom_col(position = "dodge") +
  facet_grid(USED ~ AGE, shrink = TRUE) +
  xlab("Modes associated with affective values") +
  ylab("Number of cases") +
  theme_tufte() +
  theme(panel.border = element_rect(color = "black", fill = NA)) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom",
        axis.title.x=element_blank(),
        panel.spacing = unit(0.1, "lines"),
        plot.margin = margin(0, 0, 0, 0, "cm"))

#extract legend
#https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(Freedom_by_age)

lay <- rbind(c(1, 2, 3, 4, 5, NA),
             c(6, 7, 8, 9, 10, 11),
             c(6, 7, 8, 9, 10, 12),
             c(6, 7, 8, 9, 10, 13),
             c(14, 14, 14, 14, 14, NA))

grid.arrange(textGrob(paste('FREEDOM\np-value', 
                            ifelse(round(Modes_by_Freedom_by_Age$p.value, 2) >= 0.001,
                                   paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
                                   " < 0.001")),
                      gp = gpar(fontsize = 9)),
             textGrob(paste('ENJOYMENT\np-value', 
                            ifelse(round(Modes_by_Enjoyment_by_Age$p.value, 3) >= 0.001,
                                   paste("=", round(Modes_by_Enjoyment_by_Age$p.value, 3)),
                                   " < 0.001")),
                      gp = gpar(fontsize = 9)),
             textGrob(paste('HAPPINESS\np-value', 
                            ifelse(round(Modes_by_Happiness_by_Age$p.value, 3) >= 0.001,
                                   paste("=", round(Modes_by_Happiness_by_Age$p.value, 3)),
                                   " < 0.001")),
                      gp = gpar(fontsize = 9)),
             textGrob(paste('LUXURY\np-value', 
                            ifelse(round(Modes_by_Luxury_by_Age$p.value, 3) >= 0.001,
                                   paste("=", round(Modes_by_Luxury_by_Age$p.value, 3)),
                                   " < 0.001")),
                      gp = gpar(fontsize = 9)),
             textGrob(paste('STATUS\np-value', ifelse(round(Modes_by_Status_by_Age$p.value, 3) >= 0.001,
                                                      paste("=", round(Modes_by_Status_by_Age$p.value, 3)),
                                                      " < 0.001")),
                      gp = gpar(fontsize = 9)),
             Freedom_by_age + theme(legend.position="none", 
                                    strip.text.x = element_text(angle = 90),
                                    strip.text.y = element_blank(),
                                    axis.title.y=element_blank(),
                                    axis.text.y=element_blank(),
                                    axis.ticks.y=element_blank()),
             Enjoyment_by_age + theme(legend.position="none", 
                                      strip.text.x = element_text(angle = 90),
                                      strip.text.y = element_blank(),
                                      axis.title.y=element_blank(),
                                      axis.text.y=element_blank(),
                                      axis.ticks.y=element_blank()),
             Happiness_by_age + theme(legend.position="none", 
                                      strip.text.x = element_text(angle = 90),
                                      strip.text.y = element_blank(),
                                      axis.title.y=element_blank(),
                                      axis.text.y=element_blank(),
                                      axis.ticks.y=element_blank()),
             Luxury_by_age + theme(legend.position="none", 
                                   strip.text.x = element_text(angle = 90),
                                   strip.text.y = element_blank(),
                                   axis.title.y=element_blank(),
                                   axis.text.y=element_blank(),
                                   axis.ticks.y=element_blank()),
             Status_by_age + theme(legend.position="none",
                                   strip.text.x = element_text(angle = 90),
                                   strip.text.y = element_blank(),
                                   axis.title.y=element_blank(),
                                   axis.text.y=element_blank(),
                                   axis.ticks.y=element_blank()),
             textGrob("Car",
                      rot = 270,
                      gp = gpar(fontsize = 9),
                      y = 0.2),
             textGrob("Active",
                      rot = 270,
                      gp = gpar(fontsize = 9)),
             textGrob("Public",
                      rot = 270,
                      gp = gpar(fontsize = 9),
                      y = 0.7),
             mylegend, 
             layout_matrix = lay,
             heights = c(1, 3, 3, 3, 1),
             widths = c(3, 3, 3, 3, 3, 0.5),
             left = "Proportion",
             right = "Primary Mode of Travel",
             top = "Affective Values by Age",
             bottom = "Modes Associated with Affective Values")

@@

__**Only two affective values were significant in the preceding analysis when seen from the perspective of education, namely luxury and status. As seen in Figure \ref{fig:bar-plots-by-education}, the perceptions of luxury and status are fairly consistent when differentiated by education. Most respondents tend to associate luxury and status to the use of car, albeit this association is stronger for status than for luxury. The second mode most often mentioned in relation to luxury is "other" likely due to the flexibility and convenience (but cost) of using taxis. The exception in this case is the traveller with graduate education who uses active modes. This type of respondent, while still more likely to associate luxury and status with the car, more commonly links active travel to these affects than travellers with lower levels of education. Most public transport users tend to associate luxury and status to the car, however, they associate active modes with status more than the same group with respect to luxury.**__

```{r tests-by-attribute-and-education, echo=FALSE, cache = TRUE}

# Also, use Cochran-Mantel-Haenzel tests
# Freedom
Modes_by_Freedom_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM",
                                                               USED != "Other", 
                                                               IDEAL != "Other"), 
                                                 drop.unused.levels = TRUE))

# Enjoyment
Modes_by_Enjoyment_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT",
                                                                 USED != "Other", 
                                                                 IDEAL != "Other"), 
                                                   drop.unused.levels = TRUE))

# Happiness
Modes_by_Happiness_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS",
                                                                 USED != "Other", 
                                                                 IDEAL != "Other"), 
                                                   drop.unused.levels = TRUE))

# Poverty (p = 0.827)
Modes_by_Poverty_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "POVERTY",
                                                               USED != "Other", 
                                                               IDEAL != "Other"), 
                                                 drop.unused.levels = TRUE))

# Luxury
Modes_by_Luxury_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY",
                                                              USED != "Other", 
                                                              IDEAL != "Other"), 
                                                drop.unused.levels = TRUE))

# Status
Modes_by_Status_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS",
                                                              USED != "Other", 
                                                              IDEAL != "Other"),
                                                drop.unused.levels = TRUE))
```

```{r figure-mosaic-plots-by-attribute-and-education, echo=FALSE, cache = TRUE, eval=FALSE, fig.width= 6, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}

@@

```{r figure-bar-plots-by-attribute-and-education, echo=FALSE, cache = TRUE, fig.cap="\\label{fig:bar-plots-by-education}Plots for affective values by level of education; in the y-axis is the proportion in the interval [0, 1], and the x-axis is the mode selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}

Attribute_by_ideal_by_education <- Modes_by_Attribute %>% 
  drop_na() %>%
  filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"),
         USED != "Other", 
         IDEAL != "Other") %>%
  group_by(IDEAL, ATTRIBUTE, EDUCATION, USED) %>%
  summarize(n= sum(WEIGHT)) %>%
  ungroup() %>%
  # rename(MODE = IDEAL) %>%
  mutate(CASE = "IDEAL",
         USED = factor(USED, 
                       levels = c("Car", "Active", "Public", "Other"),
                       labels = c("USED: CAR", "USED: ACTIVE", "USED: PUBLIC", "USED: OTHER")))

Attribute_by_ideal <- Attribute_by_ideal_by_education %>%
  group_by(USED, ATTRIBUTE, EDUCATION) %>%
  summarize(t = sum(n))

Attribute_by_ideal_by_education <- Attribute_by_ideal_by_education %>%
  left_join(Attribute_by_ideal, 
            by = c("USED" = "USED", 
                   "ATTRIBUTE" = "ATTRIBUTE", 
                   "EDUCATION" = "EDUCATION")) %>% 
  mutate(p = n/t)

Freedom_by_education <- ggplot(data = Attribute_by_ideal_by_education  %>% 
                           filter(ATTRIBUTE %in% c("FREEDOM"),
                                  USED != "USED: OTHER", 
                                  IDEAL != "Other"),
                         aes(x = IDEAL, y = p, fill = IDEAL)) + 
  geom_col(position = "dodge") +
  facet_grid(USED ~ EDUCATION, shrink = TRUE) +
  xlab("Modes associated with affective values") +
  ylab("Number of cases") +
  theme_tufte() +
  theme(panel.border = element_rect(color = "black", fill = NA)) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom",
        axis.title.x=element_blank(),
        legend.title = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        plot.margin = margin(0, 0, 0, 0, "cm"))
